Commutative Character Sheaves

### 2015-11-13 followup.tex
Preposition and a few references and citations.

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
this can be seen by following the argument of \cite{cunningham-roe:13a} \todo{which part of [2]?}.
Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.  \todo{Change of notation $G_0$ to $Q$}
By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.

@@

\begin{proof}
We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
This isomorphism is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2} as they apply to $\nu : a^*\cs{L}\to p^*\cs{L}$.  \todo{We seem to be missing a preposition}
It is straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
that the isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
\end{proof}

>>>>

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$; compare with \cite{cunningham-roe:13a}*{Lemma 1.4}.
Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.

@@

\begin{proof}
We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
This isomorphism is constrained by the conditions 
appearing in \eqref{E1}, \eqref{E2} and \eqref{ECS1}.
It is a straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
that the isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
\end{proof}
